---
title: "College Major vs Income"
author: "Himank Jain"
date: "27/12/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## College Major vs Income:

We try to answer below questions:

Are incomes of individuals from different majors in college differ significantly from each other or not?
If so , Which Major pays higher and which pays Lower?


```{r cars}
#devtools::install_github("jhudsl/collegeIncome")
library(collegeIncome)
#devtools::install_github("jhudsl/matahari")
library(matahari)
```

## EDA:

How does the data look like?

```{r pressure, echo=FALSE}
data(college)
head(college)
dance_start(value = FALSE, contents = FALSE)
str(college)
hist(college$median)
```
Missing Values?
and Aggregating mean of income with respect to college majors
```{r}
any(is.na(college$major_category))
factor(college$major_category)
df<-aggregate(college$median~college$major_category,FUN = mean)
names(df)<-c("major","medsal")
par(mfrow=c(1,1))
barplot(df$medsal,col='blue')
```
The Linear model:
```{r}
fit<-lm(median~major_category,data=college)
summary(fit)$coef
summary(fit)$coef[,4]<0.05
```
#the p values suggest that the medians are not significantly different.

```{r}
dance_save("college_major_analysis.rds")
dance_remove()
```
